---
output: pdf_document
---
## LIC

```{r}
U <- 1.5  # sq. meter/K building envelope conductance (assumption - 12" brick)  SI
A <- 8000  # sq. meter envelope area (assumption based on Pluto + other NYC DCAS data)  SI
V <- 37800  # cubic meter ventilation/inflitration flow rate (assumption) (1-3, step 0.5)  SI
n <- 1  # air change per hr.
rho <- 1.2  # kg/m cubed 0.00234 density of air (calc. based on IAT 68F)  SI
cp <- 0.27  # watt hrs./cubic meter in K specific heat of air (calc. based on IAT 68F)  SI
CS <- 2695  # cooling slope (from lm)
TcpC <- 62.76  # cooling CP (from CP model)
Tset <- 76  # cooling setpoint (assumption)
  

# 3PC Model
Ei <- 25200  # baseload (non-weather sensitive usage)
Toa <- 80  # sample temp. (VARIABLE)

E <- Ei + (CS * (Toa - TcpC))  # E = expected kWh at Toa - CP MODEL EQUATION
# cat(E, "=", Ei, "+ (", CS, "* (", Toa, "-", TcpC, "))" )
cat("Expected kWh at Toa:", E)

# Cooling Coefficient
CC <- ((((U * A) + (V * n * rho * cp)) / 1000) * 0.556) * (30*24) # convert from watts to kw, = kwh per F (multiply by 0.556)
cat("Cooling Coefficient:", CC)

# Efficency
Effc <- CC / (CS)
cat("Cooling efficiency:", Effc)

# Qi - sum of internal loads from electricity use, solar gain and occupants
#TcpC <- Tset - Qi / CC
Qi <- -CC * (TcpC - Tset) # Just kWh (not per degree)
cat("Internal loads:", Qi)
```

```{r}

parameters <- c(U, A, V, rho, cp, CS, TcpC, Tset, Ei, Toa, E, CC, Effc, Qi)
as.data.frame(parameters)
names(parameters) <- c('U', 'A', 'V', 'rho', 'cp', 'CS', 'TcpC', 'Tset', 'Ei', 'Toa', 'E', 'CC', 'Effc', 'Qi')
parameters <- round(parameters, 5)
parameters

```

## Simulation 
### Assumptions made for model can be simulated
### Sim #1: Toa -- use CP Model Equation and simulate Toa from 10-100 degrees F in steps of 5 degrees
### Sim #2: Tset -- substitute other values from 50 to 75, in steps of 5 degrees -- this simulates setting the thermostat lower or higher
### Sim #3: U -- substitute other values: 0.25, 0.18, 0.12, 0.09 -- this simulates adding insulation, etc. to tighten building envelope
### Sim #4: V -- substitute other values: 1 to 3, in steps of 0.5 -- this simulates improved/worse ventilation/infiltration flow rate (lower is)