---
output: pdf_document
---
## LIC

```{r}

# Function: CP Model Equation

bldg.sim <- function(oa.temp, setpoint, u.value, air.chg) {

  # Assumptions
  baseload <- 25200
  #u.value <- 1.5  # watts per sq. meter/K building envelope conductance  SI
  area <- 7500  # sq. meter envelope area  SI
  volume <- 37800  # cubic meter volume (conditioned space) (assumption) SI
  #air.chg <- 1  # air change per hr.
  rho <- 1.2  # kg/m cubed density of air  SI
  cp <- 0.27  # watt hrs./cubic meter in K specific heat of air  SI
  cool.slope <- 2695  # cooling slope (from lm)
  cool.cp <- 62.76  # cooling CP (from CP model)
  #setpoint <- 76  # cooling setpoint (assumption)
  #oa.temp
  
  # Cooling Coefficient
  cool.coef <- ((((u.value * area) + (volume * air.chg * rho * cp)) / 1000) * 0.556) * (30*24) 
  # convert from watts to kw, = kwh per F (multiply by 0.556)

  # Cooling Efficiency
  cool.eff <- cool.coef / cool.slope
  
  # Internal Loads
  i.loads <- -cool.coef * (cool.cp - setpoint)
  
  # Total Electricity
  total.e <- ifelse(oa.temp - cool.cp > 0,
    baseload + (cool.slope * (oa.temp - cool.cp)),
    baseload) # E = expected kWh at Toa - CP MODEL EQUATION

  # Parameters
  parameters <- c(u.value, area, volume, air.chg, rho, cp, cool.slope, cool.cp, 
                  cool.eff, setpoint, baseload, oa.temp, total.e, i.loads)
  # as.data.frame(parameters)
  names(parameters) <- c('u-value', 'surface area', 'volume', 'air changes', 'density of air', 
                         'specific heat of air', 'cooling slope', 'cooling change-point', 
                         'cooling efficiency', 'setpoint', 'baseload', 'outdoor air temp.', 
                         'total electricity', 'internal loads')
  
  return(cbind(total.e, cool.coef, cool.eff, i.loads))
  # Return
  #return(
  #cat("Expected kWh at Toa:", total.e, 
      #"\nCooling Coefficient:", cool.coef, 
      #"\nCooling Efficiency:", cool.eff,
      #"\nInternal Loads:", i.loads, 
      #"\nParameters\n", 
      #parameters
      
      #))
}

bldg.sim(50, 76, 1.5, 1)

```
## Simulation 
### Assumptions made for model can be simulated
### Sim #1: Toa -- use CP Model Equation and simulate Toa from 10-100 degrees F in steps of 5 degrees


The first simulation using the building changepoint model uses a temperature range from 10 to 100 deg. F by 5 degree incrememnts. All other parameters are kept constant (thermostat setpoint: 76 deg. F, u value: 1.5, air exchange: 1). 


```{r}
library(devtools)
scipen=9999

sim.temps <- seq(from = 10, to = 100, by = 5)

temp.range.results <- lapply(sim.temps, FUN = bldg.sim,  setpoint = 76, u.value = 1.5, air.chg = 1)

temp.range.results <- as.data.frame(do.call(rbind, temp.range.results))
temp.range.results <- cbind(sim.temps, temp.range.results)
print(temp.range.results)

```


```{r}
summary(temp.range.results)
```


### Sim #2: Tset -- substitute other values from 50 to 75, in steps of 5 degrees -- this simulates setting the thermostat lower or higher

The second simulation using the building changepoint model uses a thermostat temperature set range from 50 to 75 deg. F by 5 degree incrememnts. All other parameters are kept constant (temperature: 76 deg. F, u value: 1.5, air exchange: 1). 

```{r}
library(devtools)
scipen=9999

sim.Tset <- seq(from = 50, to = 75, by = 5)

Tset.range.results <- lapply(sim.Tset, FUN = bldg.sim, oa.temp = 76, u.value = 1.5, air.chg = 1)

Tset.range.results <- as.data.frame(do.call(rbind, Tset.range.results))
Tset.range.results <- cbind(sim.Tset, Tset.range.results)
print(Tset.range.results)

```


```{r}
summary(Tset.range.results)
```


### Sim #3: U -- substitute other values: 0.25, 0.18, 0.12, 0.09 -- this simulates adding insulation, etc. to tighten building envelope

The third simulation using the building changepoint model uses building insulation coefficient range from 0.09 to 0.25 by 0.1 degree incrememnts. All other parameters are kept constant (temperature: 76 deg. F, thermostat setpoint: 76 deg. F, air exchange: 1). 

```{r}

sim.insulation <- seq(from = 0.6, to = 2, by = 0.2)

insulation.range.results <- lapply(sim.insulation, FUN = bldg.sim, oa.temp = 76, setpoint = 76, air.chg = 1)

insulation.range.results <- as.data.frame(do.call(rbind, insulation.range.results))
insulation.range.results <- cbind(sim.insulation, insulation.range.results)
print(insulation.range.results)

```


```{r}
summary(insulation.range.results)
```


### Sim #4: V -- substitute other values: 1 to 3, in steps of 0.5 -- this simulates improved/worse ventilation/infiltration flow rate (lower is)


The fourth simulation using the building changepoint model uses building ventilation / infiltration flow rate range from 0.09 to 0.25 by 0.1 degree incrememnts. All other parameters are kept constant (temperature: 76 deg. F, thermostat setpoint: 76 deg. F, u value: 1.5). 


```{r}

sim.V <- seq(from = 1, to = 3, by = 0.5)

V.range.results <- lapply(sim.V, FUN = bldg.sim,  oa.temp = 76, setpoint = 76, u.value = 1.5)

V.range.results <- as.data.frame(do.call(rbind, V.range.results))
V.range.results <- cbind(sim.V, V.range.results)
print(V.range.results)

```


```{r}
summary(V.range.results)
```